\vspace{-2cm} Government websites as data: A methodological pipeline with application to the websites of municipalities in the United States

### 2018-07-20 paper/manuscript.tex
nearly finished Section 4

\subsection{Boilerplate Removal}\label{boilerplate}
% BRUCE HERE
As noted above, city websites contain a large amount of text that is uninformative for its actual content and therefore a hindrance to correct analysis by automatic text processing methods. This is a common issue with textual data in which informative content is embedded in technically structured documents. See, e.g., \citet{burgess2016legislative,wilkerson2015tracing} and \citet{linder2018text} for examples of boilerplate removal in the analysis of legislative text. In the case of websites, lines in documents are generally quite informative, so all of our boilerplate removal efforts are done at this level.

@@

\subsection*{Boilerplate Classification}
In order to determine whether a line should be discarded, we train a simple classifier. We sampled 100 lines from documents each of the following five cities: Los Angeles, CA, Indianapolis, IN, New York, NY, Shreveport, LA, and Seattle, WA. To ensure that lines which occur more frequently in these cities (sometimes hundreds of thousands of times) had a higher probability of being scrutinized by the classifier, we use sampling weights equivalent to the proportion of total lines in a city's corpus made up by each specific line type. To account for the higher likelihood of some lines being part of the training set, we use inverse probability weights in the classifier.\footnote{Note that the performance of the classifier is robust to the use of these weights and only changes by about one percentage point if they are not used.}

These 500 lines were then hand-coded as either substantively useful or useless. Then we trained a random forest with this usefulness measure as the dependent variable. The independent variables were: (1) number of times the line was duplicated within the city, (2) length of the line, in characters, (3) number of tokens in the line, and (4) the median distance from the document midpoint to the position of the line itself. The purpose of these covariates is as following:

The length of the line and the number of tokens are a way to find lines consisting of only a word or two. This is highly predictive of lines which are used as website headers and navigational elements, which are of of zero substantive interest to us. These terms also happen to be fairly common, which causes them to be overweighted by the topic model.

To directly address the latter problem, a measure for the number of times a line is duplicated within a city is included. Many lines occur hundreds or even thousands of times on a single website, and therefore are terms that are highly predictive of the website, which causes the topic model to create topics that are highly correlated with cities.

Finally, the distance measure: Since boilerplate terms such as navigational elements, headers, footers, and so on, should occur more frequently at the beginning and the end of websites, we attempt to identify such content as following: We measure the distance between the midpoint of a document and the position of a line, expressed as quantiles (to account for differing document lengths). Since lines can occur in multiple documents, or multiple times in the same document, we take the median of these measures. Thus, for example, a line which often occurs at the beginning of documents might have a score of 0.45, whereas a line that tends to be found more in the center, and thus be indicative of more relevant content, might be scored with a 0.11 instead.

>>>>

\subsection{Boilerplate Removal}\label{boilerplate}
As noted above, city websites contain a large amount of text that is uninformative for its actual content and therefore a hindrance to correct analysis by automatic text processing methods. This is a common issue with textual data in which informative content is embedded in technically structured documents. See, e.g., \citet{burgess2016legislative,wilkerson2015tracing} and \citet{linder2018text} for examples of boilerplate removal in the analysis of legislative text. In the case of websites, lines in documents are generally quite informative, so all of our boilerplate removal efforts are done at the line level.

@@

\subsection*{Boilerplate Classification}
In order to determine whether a line should be discarded, we train a classifier on a human-coded sample. We sampled 100 lines from documents in each of the following five cities: Los Angeles, CA, Indianapolis, IN, New York, NY, Shreveport, LA, and Seattle, WA. To ensure that lines which occur more frequently in these cities (sometimes hundreds of thousands of times) had a higher probability of being scrutinized by the classifier, we use sampling weights equivalent to the proportion of total lines in a city's corpus made up by each specific line type [@markus, please add an example here of a line that occurs a lot (e.g., "abc def" occurs in X documents in LA) to help the reader understand the concept of boilerplate lines happening frequently]. To account for the higher likelihood of some lines being part of the training set, we use inverse probability weights in training the classifier---the weight of each line in the sample is 1/[number of occurrences in the corpus].\footnote{Note that the performance of the classifier is robust to the use of these weights and only changes by about one percentage point if they are not used.}

These 500 lines were then hand-coded as either substantively informative or not [@markus, how many were coded as boilerplate?]. We then trained a number of different classifiers with this informativeness measure as the dependent variable. The independent variables we use are: (1) number of times the line was duplicated within the city, (2) the length of the line, in characters, (3) the number of tokens in the line, and (4) the median distance from the document midpoint to the position of the line itself. The purpose of these covariates is as follows:

% BRUCE HERE
\begin{itemize}
\item The length of the line and the number of tokens are a way to find lines consisting of only a word or two. This is highly predictive of lines which are used as website headers and navigational elements, which are of of zero substantive interest to us. These terms also happen to be fairly common, which causes them to be overweighted by the topic model.

\item To directly address the latter problem, a measure for the number of times a line is duplicated within a city is included. Many lines occur hundreds or even thousands of times on a single website, and therefore are terms that are highly predictive of the website, which causes the topic model to create topics that are highly correlated with cities.

\item Finally, the distance measure: Since boilerplate terms such as navigational elements, headers, footers, and so on, should occur more frequently at the beginning and the end of websites, we attempt to identify such content as following: We measure the distance between the midpoint of a document and the position of a line, expressed as quantiles (to account for differing document lengths). Since lines can occur in multiple documents, or multiple times in the same document, we take the median of these measures. Thus, for example, a line which often occurs at the beginning of documents might have a score of 0.45, whereas a line that tends to be found more in the center, and thus be indicative of more relevant content, might be scored with a 0.11 instead.
\end{itemize}
